---
title: "Presentation 1"
author: "Georges Bressange"
date: "21/12/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide
Some content.

*** 
A slide without a title.

## Title of the slide

- Bullet 1
- Bullet 2

1. Item a
2. Item b

###  top level 

## New slide

Plain text

*italic*

**bold**

`for (i %in% 1:10)`

## New slide

```{r}
head(mtcars)
```

```{r, comment = ""}
head(mtcars )
```

## New slide with echo TRUE

```{r, comment = "", echo = TRUE}
head(mtcars )
```

## New slide with code and no evaluation

```{r, comment = "", echo = TRUE, eval = FALSE}
head(mtcars )
```

## New slide with a plot without code

```{r, fig.align='center', fig.cap="My incredible figure"}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```

## New slide with a plot with code

```{r, echo = TRUE}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```

## New slide with code without the plot

```{r, echo = TRUE, eval = FALSE}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

